---
title: "report_child_meta"
output:
  pdf_document:
    latex_engine: pdflatex
    toc: true
    number_sections: true
    df_print: kable
mainfont: Arial
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
  - \usepackage{threeparttablex}
  - \usepackage[normalem]{ulem}
  - \usepackage{makecell}
params:
  metareg_k: NA
  metareg_df_coeff: NA
  metareg_mods: NA
  metareg_QE: NA
  metareg_QEp: NA
  metareg_QM: NA
  metareg_QMp: NA
  metareg_QM_knha: NA
  metareg_QMp_knha: NA
  metareg_tau2: NA
  metareg_se.tau2: NA
  metareg_I2: NA
  metareg_H2: NA
  metareg_R2: NA
---

# Meta-Regression

## Model Type

Mixed-Effects Model (k = `r params$metareg_k`; $\tau$^2^ estimator: `r params$estim`)

## Model Coefficients

```{r table_metareg, echo = FALSE}
library(kableExtra)
library(data.table)

df <- as.data.table(params$metareg_df_coeff$res)

kableExtra::kbl(df, booktabs = TRUE, digits = 2, caption = "Model coefficients without Knapp-Hartung-adjustment",
                position = "h") %>%
      kable_styling("striped")


```

Intercept Model with Knapp-Hartung-adjusted standard errors: 
```{r table_metareg_knha, echo = FALSE}
library(kableExtra)
library(data.table)

df <- as.data.table(params$metareg_df_coeff$res_knha)

kableExtra::kbl(df, booktabs = TRUE, digits = 2, caption = "Model coefficients with Knapp-Hartung-adjustment",
                position = "h") %>%
      kable_styling("striped")
```



## Test for Residual Heterogeneity

Q(df = `r params$metareg_k - params$metareg_mods`) = `r round(params$metareg_QE, 4)`, _p_ `r if(params$metareg_QEp < 0.0001){paste("< .0001")} else {paste("= ", format(round(params$metareg_QEp, 4), scientific = FALSE))}`

## Test of Moderators

QM(df = `r params$metareg_mods - 1`) = `r round(params$metareg_QM, 4)`, _p_ `r if(params$metareg_QMp < 0.0001){paste("< .0001")} else {paste("= ", format(round(params$metareg_QMp, 4), scientific = FALSE))}`.

### With Knapp-Hartung-Adjustment: 

F (df1 = `r params$metareg_mods`, df2 = `r params$metareg_k - params$metareg_mods`) = `r round(params$metareg_QM_knha, 4)`, _p_`r if(params$metareg_QMp_knha < 0.0001){paste("< .0001")} else {paste("= ", format(round(params$metareg_QMp_knha, 4), scientific = FALSE))}`.

## Heterogeneity Statistics

$\tau$^2^ (estimated amount of residual heterogeneity): `r round(params$metareg_tau2, 4)` (SE = `r round(params$metareg_se.tau2, 4)`)

I^2^ (residual heterogeneity/unaccounted variability): `r round(params$metareg_I2, 2)`%

H^2^ (unaccounted variability/sampling variability): `r round(params$metareg_H2, 2)`

R^2^ (amount of heterogeneity accounted for): `r round(params$metareg_R2, 2)`%
